SimBio: a static typing, modern Python package to simulate reaction networks

### 2023-10-30 article.qmd
Improve writing

The code to define and simulate reaction systems
is split into three Python packages:
symbolite, to create symbolic expressions;
poincaré, to define dynamical systems;
and simbio, to define reaction systems
and interface with systems biology standards such as SBML.

@@

Symbolite is a lightweight symbolics package
to create and inspect mathematical expressions,
which can be compiled to different backends.
Currently, we have implementations for NumPy, SymPy and JAX,
but it is easy to add new backends.

@@

Poincare is a package to define and simulate dynamical systems.
It provides a `System` class,
where we can define `Constant`s, `Parameter`s and `Variable`s,
and create equations linking a variable's derivative with an expression:

@@

It allows to define higher-order systems
by assigning an initial condition to a derivative:

>>>>

Modular code architecture enhances reusability, extendability and maintainability for the community.
Hence, we split the code to define and simulate reaction systems into three Python packages:
symbolite, to create symbolic expressions;
poincaré, to define dynamical systems;
and simbio, to define reaction systems
and interface with systems biology standards such as SBML.

@@

Symbolite is a lightweight symbolics package to create algebraic mathematical expressions.
They can be inspected and compiled to different backends.
Currently, we have implementations for NumPy (and Numba), SymPy and JAX,
but it is easy to add new backends.

@@

Poincare is a package to define and simulate dynamical systems.
It provides a `System` class,
where we can define `Constant`s, `Parameter`s, `Variable`s,
and create equations linking a variable's derivative with an expression:

@@

It allows to define higher-order systems
by assigning an initial condition to a `Derivative`:
